Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2019-10-03 cover_letter/cover_letter.tex

Please see our manuscript \textbf{Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields} submitted for possible publication in the \emph{Annals of Applied Statistics} (AOAS).\\*

@@

\begin{quote}
\textit{where and when should we measure in order to effectively measure a phenomenon or process taking place in the ocean?}      
\end{quote}{}

The research presented aims to address this central question by combining statistical models and methodology with autonomous robotic sensing platforms. A central effort is the introduction of informative descriptions of spatial characteristics of ocean phenomena that greatly improve how sequential data collection can be conducted. Specifically, we present a design criterion based on reducing uncertainty in the joint excursions of random fields, and derive analytical expressions for the expected Bernoulli variance reduction in the excursion set of spatial temperature and salinity variables. The proposed methodology is deployed and tested in a full-scale deployment where an autonomous underwater vehicle is tasked with mapping a river plume.

The combined study demonstrate the potential of statistics applied to support autonomous robotic decision making, representing methods and approaches with a substantial potential for further integration, which are necessary and critical to understand our changing oceans. 
\vspace{1em}

>>>>

Please see our manuscript \textbf{Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets} submitted for possible publication in the \emph{Annals of Applied Statistics} (AOAS).\\*

@@

\begin{quote}
\textit{where, when, and how should we gather information in order to effectively characterize a phenomenon in the ocean?}  
\end{quote}{}

The research presented aims to address this central question by combining statistical models and methodology with autonomous robotic sensing platforms. A central effort is the introduction of informative descriptions of spatial characteristics of ocean phenomena that greatly improve how sequential data collection can be conducted. Specifically, we present a design criterion based on reducing uncertainty in the joint excursions of random fields, and derive analytical expressions for the expected Bernoulli variance reduction in the excursion set of spatial temperature and salinity variables. The proposed methodology is deployed and tested in a full-scale deployment where an autonomous underwater vehicle is used to map a river plume.

This interdisciplinary study demonstrates the potential of statistics applied to support autonomous robotic decision making, representing methods and approaches with a substantial potential for further integration, which are necessary and critical to understand our changing oceans. 
\vspace{1em}
